The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-01-10 paper/draft.tex
additions to intro and disc

%%TODO: here come a list of processes with examples

@@

@@

>>>>

%%TODO: here come a list of processes with examples
%% - genetic processes in general
%% - isolation processes

@@

For example, the rapid switching of pollinator syndromes in species of the genus \textit{Petunia} %use package for this!
seems to be a consequence of the tight genetic linkage between loci for pollination syndrome traits (Hermann et al. 2013) % cite properly!

@@

In reality linkage between genes is not a binary decision, but rather a consequence of the distance between those genes.
The larger the distance, the higher the probability of crossing over during meiosis.
The size of the resulting genomic blocks or islands, however, may increase to several megabases in diverging population ---
a phenomenom coined as ``divergence hitchhiking'' (Via \& West 2008). % cite properly!
This mechanism is thought to facilitate sympatric speciation by reducing the detrimental effects of gene flow and
recombination between populations to speciation (Via 2011, but see Feder \& Nosil 2010).
During incipient speciation, however, th
